Mossy_custom_mrmr

### 2024-11-22 code/R/MossyPond_Custom_mrmr_TVD.Rmd
create comparison table and plot with updated classic model

```{r}
library(dplyr)
library(readr)
library(tibble)
library(cmdstanr)
library(mrmr)
library(ggpubr)
```

@@

```{r}
# pull generated quantities from model fit summary
N_classic <- classic_mod_54188_summary[, c(1,2,4)]
N_custom <- custom_mod_54188_summary[33659:33674, c(1,2,4)]
B_classic <- classic_mod_54188_summary[4221:4225, c(1,2,4)]
B_custom <- custom_mod_54188_summary[33676:33691, c(1,2,4)]
Phi_classic <- classic_mod_54188_summary[4240:4243, c(1,2,4)]
Phi_custom <- custom_mod_54188_summary[33739:33753, c(1,2,4)]
p_classic <- classic_mod_54188_summary[4226:4239, c(1,2,4)]
p_custom <- custom_mod_54188_summary[33692:33738, c(1,2,4)]

@@

print(GenQuant_comparison_mp)

@@

>>>>

```{r}
library(dplyr)
library(readr)
library(tibble)
library(cmdstanr)
library(mrmr)
library(ggpubr)
library(gridExtra)
library(grid)
```

@@

```{r}
# pull generated quantities from model fit summary
N_classic <- classic_mod_mp_summary[33613:33628, c(1,2,4)]
N_custom <- custom_mod_mp_summary[33658:33674, c(1,2,4)]
B_classic <- classic_mod_mp_summary[33629:33644, c(1,2,4)]
B_custom <- custom_mod_mp_summary[33675:33690, c(1,2,4)]
Phi_classic <- classic_mod_mp_summary[33692:33706, c(1,2,4)]
Phi_custom <- custom_mod_mp_summary[33738:33752, c(1,2,4)]
p_classic <- classic_mod_mp_summary[33645:33691, c(1,2,4)]
p_custom <- custom_mod_mp_summary[33691:33737, c(1,2,4)]

@@

View(GenQuant_comparison_mp)

@@

  View(custom_mod_mp_summary)
